\documentclass[10pt]{article}
\usepackage{a4wide}
\usepackage{ifpdf}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb}
\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage[compact]{titlesec}

\newenvironment{packed_items}{
    \begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
}{\end{itemize}}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\begin{document}
    \begin{centering}
        {\LARGE William George Looman}
        
        {\today}
        
        {
            \begin{tabularx}{\textwidth}{lXr}
            220 Riccarton Road  &  &                Skype: tioraplace \\
            Upper Riccarton     &  &              Home: (03) 669 3669 \\
            Christchurch, 8041  &  &             Mobile: 027 738 4883 \\
            New Zealand         &  & Email: ghostunderscore@gmail.com \\
            \end{tabularx}
        }
    \end{centering}
    \section*{Profile}\small
    \vspace{-5pt}
        I am a dedicated worker able to work well individually or as part of a team. I have a good grounding in Java, C\#, C and C++ with a little experience in python and \LaTeX\, and can pick up new computer languages quickly. I have built 4+ computers for myself and others; in building these computers I personally selected compatible parts, connected it all together and installed appropriate operating systems, drivers and software. I have had experience in setting up network, RAID/LVM’s and virtualising machines under both Windows and Linux.
    \subsection*{Strengths}
        \begin{packed_items}\small
            \item{High level of technical skills relating to the IT industry.}
            \item{Quick learner, especially for any computer related activities.}
        \end{packed_items}
    \section*{Current Course of Study}
    \vspace{-7pt}
        \subsubsection*{Bachelor of Engineering with Honours at University of Canterbury.}
            {\rowcolors{1}{white}{lightgray}\footnotesize
            \begin{tabularx}{\textwidth}{llXl}
                \hline
                \textbf{Year} & \textbf{Course} & & \\
                \hline
                2010 & COSC324 & Advanced Software Engineering                      & A    \\
                2010 & COSC329 & Algorithms and Artificial Intelligence             & A+   \\
                2010 & COSC332 & Data and Network Security                          &      \\
                2010 & COSC363 & Computer Graphics                                  &      \\
                2010 & ENEL334 & Electronic Device Engineering                      &      \\
                2010 & ENEL350 & Design and Management 2                            &      \\
                2010 & ENEL351 & Signals, Systems and Control                       &      \\
                2010 & ENEL353 & Computer Hardware Engineering I                    &      \\
                2009 & COSC224 & Introduction to Software Engineering               & A+   \\
                2009 & COSC225 & Human-Computer Interaction                         & A-   \\
                2009 & COSC227 & Probabilistic Methods and Information Theory       & A+   \\
                2009 & COSC231 & Introduction to Data Communications                & A+   \\
                2009 & ENCE208 & C Programming                                      & A+   \\
                2009 & ENCE221 & Introduction to Computer Systems                   & A+   \\
                2009 & ENEL202 & Circuits and Systems                               & A+   \\
                2009 & ENEL203 & Principles of Electronics                          & A    \\
                2009 & ENEL211 & Design and Management 1                            & Pass \\
                \hline
            \end{tabularx}
            }

    \section*{Computer/IT Employment History}
        \subsubsection*{2009-2010 \quad Summer Studentship \quad Plant and Food}\small
            Responsibilities:
            \begin{packed_items}
                \item{Design a farm irrigation calculator based off a spreadsheet prototype.}
                \item{Implement the design in C\#.}
                \item{Self manage the design and implementation of this program.}
                \item{Document the program.}
            \end{packed_items}
        \subsubsection*{2008-2009 \quad Casual Worker \quad Canterbury University Centre for Teaching And Learning}\small
            Responsibilities:
            \begin{packed_items}
                \item{Support work around the new Moodle Implementation.}
                \item{Help run workshops teaching lecturers to use Moodle.}
                \item{Manage workflow within tasks assigned.}
                \item{Keep good records of work done, issues encountered, etc. and maintain confidentiality at all times.}
            \end{packed_items}
    \section*{Additional Work Experience}
        \subsubsection*{2005-2008\quad Crew Member \quad McDonalds Family Restaurant Blenheim}\small
            Responsibilities:
            \begin{packed_items}
                \item{Worked as part of a team to serve hot, fresh food on time to customers.}
                \item{Served customers, ensuring that service was fast, accurate and pleasing.}
            \end{packed_items}
        \subsubsection*{2002-2008 \quad Paper Boy \quad Marlborough Express}\small
            Responsibilities:
            \begin{packed_items}
                \item{Delivered papers on time 6 days a week.}
                \item{Ensured that client base was kept happy.}
            \end{packed_items}
    \section*{Education}
    {\footnotesize\rowcolors{1}{white}{lightgray}
        \begin{tabularx}{\textwidth}{llXl|l}
            \hline
            \textbf{Year} & \textbf{Course} & & & \textbf{School/Institution} \\
            \hline
            2008 & COSC229 & Algorithms                                         & A+ & Canterbury University\\
            2008 & EMTH171 & Mathematical Modelling and Computation             & A+ & Canterbury University\\
            2008 & ENGR101 & Foundations of Engineering                         & A  & Canterbury University\\
            2008 & MATH254 & Linear Algebra 2                                   & A+ & Canterbury University\\
            2008 & MATH264 & Multivariate Calculus and Differential Equations   & A  & Canterbury University\\
            2008 & PHYS113 & Waves, Thermodynamics and Materials                & A+ & Canterbury University\\
            2008 & PHYS114 & Electrical and Quantum Physics                     & A+ & Canterbury University\\
            \hline
            2007 & MATH199           & Advancing in Mathematical Sciences       & A+ & Canterbury University\\
            2007 & 159.101           & Programming Fundamentals.                             & A+ & Massey University         \\
            2007 & 159.102           & Computer Science Fundamentals.                        & A+ & Massey University\\
            2007 & Level Three NCEA: & Statistics and Modelling, Physics, Chemistry.         &    & Marlborough Boys’ College \\
            \hline
            2006 & Level Three NCEA: & Mathematics with Calculus, Computing.                 &    & Marlborough Boys’ College \\
            2006 & Level Two NCEA:   & Physics, Chemistry, Accounting, Electronics, English. &    & Marlborough Boys’ College \\
            \hline
            2005 & Level Two NCEA:   & Mathematics, Computing.                               &    & Marlborough Boys’ College \\
            2005 & Level One NCEA:   & Science, Accounting, English, French.                 &    & Marlborough Boys’ College \\
            \hline
            2004 & Level One NCEA:   & Mathematics.                                          &    & Marlborough Boys’ College \\
            \hline
        \end{tabularx}
    }
    \section*{Achievements}
        \begin{packed_items}
            \item{I was selected for the National Science and Technology Forum, held in Auckland in January 2007.}
            \item{I am Proximae Accessit for 2007 at Marlborough Boys’ College.}
            \item{I achieved NCEA scholarships in Physics and Statistics with Modelling and got outstanding in Mathematics with Calculus in 2007.}
            \item{I was awarded the National Certificate of Educational Achievement (level 3), achieved with merit in 2007 and levels 1 and 2 in 2005.}
            \item{I achieved the pre-requisites for National Certificate in Computing (level 3) and National Certificate in Electronics Technology (level 2) in 2006.}
            \item{I was awarded the Koru Award for my outstanding performance during the 2009/2010 Summer Studentship programme at Plant \& Food Research.}
        \end{packed_items}
    \section*{Referees}
        \begin{tabularx}{\textwidth}{XX}
            Dr. Hamish Brown                & Derek Chirnside                                    \\
            \emph{Scientist}                & \emph{Organisational Learning Contractor}          \\
            The New Zealand Institute for   & Formerly:                                          \\
            Plant and Food Research Limited & \qquad \emph{Senior Educational Designer}          \\
            Private Bag 4704, Christchurch  & \qquad University Centre for Teaching and Learning \\
            (03) 325 9394                   & \qquad University of Canterbury                    \\
            027 226 1166                    & 021 511 303                                        \\
            Hamish.Brown@plantandfood.co.nz & derek.chirnside@gmail.com                          \\
        \end{tabularx}

\end{document}
