\documentclass[10pt,a4]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amsthm, amssymb}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{url}
\usepackage{hyperref}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{parcolumns} % NOTE: This is a customised version in this directory.
% It was changed to remove all start of paragraph indentation.
\usepackage[sc]{titlesec}
\usepackage{ragged2e}

\hypersetup{
  pdfborder = {0 0 0}
}

\newenvironment{packed_items}{
  \ignorespaces
  \begin{itemize}
  \small
}{
  \end{itemize}
  \ignorespacesafterend
}

\definecolor{black}{rgb}{0,0,0}
\definecolor{dark}{rgb}{0.3,0.3,0.3}
\definecolor{grey}{rgb}{0.4,0.4,0.4}

\newcommand{\leftstyle}[1]{\raggedleft{\color{black}\Large\scshape#1}}
\newcommand{\rightstyle}{\raggedright\color{grey}}
\newcommand{\rightheadingstyle}[1]{{\color{dark}\large\scshape#1}\color{grey}}
\newcommand{\sect}[2]{
  \colchunk{\leftstyle{#1}}
  \colchunk{\rightstyle#2}
  \colplacechunks
  \vspace{20pt}
}

\renewcommand{\labelitemii}{$\circ$}

\begin{document}
  \begin{parcolumns}[colwidths={1=0.3\textwidth},nofirstindent]{3}
    \colchunk{\leftstyle{
      \LARGE \textbf{W}im \textbf{L}ooman
      \vspace{5pt}
      \large \today
    }}
    \colchunk{\rightstyle
      43 Lynfield Ave, Ilam \\
      Christchurch, 8041 \\
      New Zealand
    }
    \colchunk{\rightstyle\raggedleft
      +64 27 738 4883 \\
      \href{mailto:ghostunderscore@gmail.com}{\nolinkurl{ghostunderscore@gmail.com}} \\
      \url{https://github.com/Nemo157}
    }
    \colplacechunks
    \vspace{20pt}
  \end{parcolumns}

  \begin{parcolumns}[colwidths={1=0.3\textwidth},nofirstindent]{2}

    \sect{
      Profile
    } { \justifying
      I am a dedicated worker able to work well individually or as part of a
      team. I have a good grounding in Ruby, Python, Java, C\#, C and C++ with a little
      experience in \LaTeX\, \& Erlang and can pick up new computer languages
      quickly.
    }

    \sect{
      Strengths
    } {
      High level of technical skills relating to the IT industry.

      Quick learner, especially for any computer related activities.
    }

    \sect{
      Employment
    } {
      \rightheadingstyle{University of Canterbury \hfill 2011}

      \rightheadingstyle{\normalsize Computer Science and Software Engineering Tutoring}
      \begin{packed_items}
        \item{Tutoring undergraduate computer science students.}
        \item{Courses tutored:}
        \begin{packed_items}
          \item{COSC121 --- Introduction to Computer Programming}
          \item{ENCE260 --- Computer Systems}
        \end{packed_items}
      \end{packed_items}

      \rightheadingstyle{Tait Electronics Ltd \hfill 2010 -- 2011}
      \begin{packed_items}
        \item{Transform a tool from an internal protocol to utilise SNMP.}
        \item{Update SharpSNMP to support parsing more MIB data.}
        \item{Write a python utility to generate C mapping code from a set of XML, and config files.}
        \item{Write good accurate documentation on all changes.}
      \end{packed_items}

      \rightheadingstyle{Plant and Food Research Ltd \hfill 2009 -- 2010}
      \begin{packed_items}
        \item{Design a farm irrigation calculator based off a spreadsheet prototype.}
        \item{Implement the design in C\#.}
        \item{Self manage the design and implementation of this program.}
        \item{Document the program.}
      \end{packed_items}

      \rightheadingstyle{University of Canterbury \hfill 2008 -- 2009}

      \rightheadingstyle{\normalsize University Centre for Teaching and Learning}
      \begin{packed_items}
        \item{Support work around the new Moodle Implementation.}
        \item{Help run workshops teaching lecturers to use Moodle.}
        \item{Keep good records of work done, issues encountered, etc.}
        \item{Maintain confidentiality at all times.}
      \end{packed_items}
    }

    \sect{
      Open Source
    } {
      \rightheadingstyle{SharpSNMP\footnotemark}
      \begin{packed_items}
        \item{Updated the MIB parser to support parsing more of the information contained\footnotemark.}
      \end{packed_items}
        
      \rightheadingstyle{Rubinius\footnotemark}
      \begin{packed_items}
        \item{Small fix to some tests, hopefully more to come.}
      \end{packed_items}
    }

    \footnotetext[1]{\url{http://sharpsnmplib.codeplex.com/}}
    \footnotetext{Change documentation: \url{http://db.tt/0nphrIa}}
    \footnotetext{\url{http://rubini.us/}}

    \newpage

    \sect{
      Study
    } {
      \rightheadingstyle{\normalsize 4th year of BE(Hons) at the University of Canterbury}

      \color{dark}
      \rowcolors{1}{white}{lightgray}\footnotesize
      \begin{tabularx}{0.7\textwidth}{llXl}
        \hline
        \textbf{Year} & \textbf{Course} & & \\
        \hline
        2011 & COSC428 & Computer Vision                                    &      \\
        2011 & COSC422 & Advanced Computer Graphics                         &      \\
        2011 & COSC401 & Machine Learning                                   &      \\
        2011 & ENCE427 & Computer Engineering Project                       &      \\
        2011 & ENEL429 & Computer Hardware Engineering 2                    &      \\
        2011 & ENEL430 & Control Systems                                    &      \\
        2011 & ENEL438 & Engineering Economics and Management               &      \\
        2010 & COSC324 & Advanced Software Engineering                      & A    \\
        2010 & COSC329 & Algorithms and Artificial Intelligence             & A+   \\
        2010 & COSC332 & Data and Network Security                          & A    \\
        2010 & COSC363 & Computer Graphics                                  & A+   \\
        2010 & ENEL334 & Electronic Device Engineering                      & B    \\
        2010 & ENEL350 & Design and Management 2                            & A-   \\
        2010 & ENEL351 & Signals, Systems and Control                       & A+   \\
        2010 & ENEL353 & Computer Hardware Engineering I                    & A+   \\
        2009 & COSC224 & Introduction to Software Engineering               & A+   \\
        2009 & COSC225 & Human-Computer Interaction                         & A-   \\
        2009 & COSC227 & Probabilistic Methods and Information Theory       & A+   \\
        2009 & COSC231 & Introduction to Data Communications                & A+   \\
        2009 & ENCE208 & C Programming                                      & A+   \\
        2009 & ENCE221 & Introduction to Computer Systems                   & A+   \\
        2009 & ENEL202 & Circuits and Systems                               & A+   \\
        2009 & ENEL203 & Principles of Electronics                          & A    \\
        2009 & ENEL211 & Design and Management 1                            & Pass \\
        \hline
      \end{tabularx}
    }

    \sect{
      Achievements
    } {
      \vspace{-22pt}
      \begin{packed_items}
        \item{I was selected for the National Science and Technology Forum, held in Auckland in January 2007.}
        \item{I was awarded Proximae Accessit for 2007 at Marlborough Boys’ College.}
        \item{I achieved NCEA scholarships in Physics and Statistics with Modelling and got outstanding in Mathematics with Calculus in 2007.}
        \item{I was awarded the National Certificate of Educational Achievement (level 3), achieved with merit in 2007 and levels 1 and 2 in 2005.}
        \item{I achieved the pre-requisites for National Certificate in Computing (level 3) and National Certificate in Electronics Technology (level 2) in 2006.}
        \item{I was awarded the Koru Award for my outstanding performance during the 2009/2010 Summer Studentship programme at Plant \& Food Research.}
      \end{packed_items}
    }

    \sect{
      Interests
    } {
      Hockey, cycling, modern jive, hobby embedded development, video games.
    }
  \end{parcolumns}

  \begin{parcolumns}[colwidths={1=0.3\textwidth,2=0.35\textwidth},nofirstindent]{3}
    \colchunk{ \leftstyle{
      Referees
    }}

    \colchunk{ \rightstyle
      \hspace{-3.5pt}Dr. Hamish Brown \\
      \emph{Scientist}
    }

    \colchunk{ \rightstyle
      \hspace{-3.5pt}Joe Osman \\
      \emph{Design Engineer}
    }

    \colplacechunks \vspace{10pt}

    \colchunk[2]{ \rightstyle
      \hspace{-3.5pt}The New Zealand Institute for \\
      Plant and Food Research Limited \\
      Private Bag 4704 \\
      Christchurch \\
      New Zealand
    }

    \colchunk{ \rightstyle
      \hspace{-3.5pt}Tait Radio Communications \\
      175 Roydvale Avenue \\
      Christchurch \\
      New Zealand
    }

    \colplacechunks \vspace{10pt}

    \colchunk[2]{ \rightstyle
      \hspace{-3.5pt}+64 3 325 9394 \\
      +64 27 226 1166 \\
      \url{hamish.brown@plantandfood.co.nz}
    }

    \colchunk{ \rightstyle
      \hspace{-3.5pt}+64 3 357 1584 \\
      +64 21 217 4503 \\
      \url{joe.osman@taitradio.com}
    }

    \colplacechunks \vspace{10pt}
  \end{parcolumns}
\end{document}
